Report

### 2021-05-28 Rmd/report.Rmd
Merge report.Rmd from both branches

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-')

@@

@@

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant)), alpha = 0.5) +
	geom_point(size = 2, alpha = 0.5) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	scale_colour_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	) +
	ggsave(here("Figures", "cohort.png"))
```

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "participants_attrition.png"))
```

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(valid_status = case_when(
		!valid_vocab ~ "Invalid vocabulary",
		!valid_gaze ~ "Invalid gaze",
		!valid_other ~ "Other",
		!valid_participant ~ "Invalid participant",
		TRUE ~ "Valid"
	)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_color_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme_bilingual() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1),
		axis.text.y = element_text(size = 8),
		axis.title.y = element_blank()
	)
```

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_bilingual() +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

@@

```
elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
	(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant) +
	(1 + ot1 + ot2 + ot3 + trial_type + age_group + lp | target)
```

@@

VarCorr(fit)$participant %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
	ggplot(aes(term1, term2, fill = value)) +
	geom_tile() +
	coord_fixed() +
	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
	scale_fill_distiller(palette = "Oranges") +
	theme_bilingual() +
	theme(
		axis.title = element_blank(),
		axis.text.x = element_text(angle = 90)
	)

@@

#### Marginal means

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
y_pred <- logit_to_prob(predict(fit))

gaze %>% 
	drop_na() %>% 
	ggplot(aes(x = ot1, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = y_pred), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = y_pred), geom = "line", size = 1) +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type") +
	scale_color_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_bw() +
	theme(
		legend.position = "top",
		panel.background = element_rect(fill = "white", colour = NA),
		strip.background = element_rect(colour = "grey"),
		panel.border = element_rect(colour = "grey"),
		panel.grid = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 7)
	)
```

@@

# Appendix

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-',
		ggplot2.discrete.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.discrete.colour = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.continuous.fill = RColorBrewer::brewer.pal(6, name = "Dark2"),
		ggplot2.continuous.colour = RColorBrewer::brewer.pal(6, name = "Dark2")
)

@@

theme_custom <- function(){
	theme(
		panel.background = element_rect(fill = "transparent"),
		panel.grid = element_blank(),
		#panel.grid = element_line(colour = "grey", linetype = "dotted"),
		panel.border = element_rect(fill = "transparent", colour = "black"),
		text = element_text(colour = "black", size = 15),
		axis.text = element_text(colour = "black")
	)
}
theme_set(theme_custom())

@@

```{r participants_summary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	ggplot(aes(lp, fill = as.factor(test_language))) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Test language") +
	theme(
		legend.position = "top",
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "sample.png"))

@@

```{r participants_cohort, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	) +
	ggsave(here("Figures", "cohort.png"))
```

@@

```{r participants_cdi, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
participants %>% 
	left_join(distinct(attrition, participant, valid_participant)) %>% 
	drop_na(valid_participant) %>% 
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		)
	) %>% 
	ggplot(aes(lp, fill = valid_status)) +
	facet_grid(location~age_group, scales = "free") +
	geom_bar(colour = NA) +
	geom_hline(yintercept = 24, linetype = "dashed") +
	scale_colour_brewer(palette = "Set1") +
	labs(x = "Group", y = "Sample size", fill = "Valid?") +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.title.x = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.title.y = element_text(angle = 90)
	) +
	ggsave(here("Figures", "participants_attrition.png"))
```

@@

```{r trials_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants, participant, location)) %>% 
	mutate(valid_status = case_when(
		!valid_vocab ~ "Invalid vocabulary",
		!valid_gaze ~ "Invalid gaze",
		!valid_other ~ "Other",
		!valid_participant ~ "Invalid participant",
		TRUE ~ "Valid"
	)) %>% 
	count(location, lp, age_group, trial_type, valid_status) %>% 
	ggplot(aes(trial_type, n, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_col(position = position_fill()) +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	scale_y_continuous(labels = scales::percent) +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(angle = 20, hjust = 1),
		axis.text.y = element_text(size = 8),
		axis.title.y = element_blank()
	)
```

@@

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
sample_size <- participants %>% 
	count(age_group, location)

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
		geom_text(data = sample_size,
			  aes(x = 1.5, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

```{r gaze_trial_age, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	count(age_group, lp)

gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
	geom_text(data = sample_size,
			  aes(x = 1, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

#### Model details

@@

```
elog ~ age_group + trial_type * lp * (ot1 + ot2 + ot3) +
(1 + ot1 + ot2 + ot3 + trial_type + age_group | participant)
```

@@

VarCorr(fit)$participant %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = "value") %>% 
	ggplot(aes(term1, term2, fill = value)) +
	geom_tile() +
	coord_fixed() +
	labs(x = "Term 1", y = "Term 2", fill = "Covariance") +
	scale_fill_viridis_c() +
	theme(
		axis.title = element_blank(),
		axis.text.x = element_text(angle = 90)
	)

@@

#### Marginal means {.tabset .tab-pills}

##### Overall

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
y_pred <- logit_to_prob(predict(fit))
sample_size <- participants %>% 
	filter(valid_participant) %>%
	count(age_group, lp)

gaze %>% 
	drop_na() %>% 
	ggplot(aes(x = ot1, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = y_pred), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = y_pred), geom = "line", size = 1) +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By vocabulary size

```{r gaze_time_vocab_lower, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size <= median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size <= median(.$vocab_size)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size <= median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_vocab_upper, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(vocab_size > median(.$vocab_size, na.rm = TRUE), valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(vocab_size > median(.$vocab_size)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Vocabulary size > median") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

##### By location

```{r gaze_time_location_barcelona, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Barcelona", valid_participant) %>% 
	count(age_group, lp)

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Barcelona") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Barcelona") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

```{r gaze_time_location_oxford, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(location=="Oxford") %>% 
	count(age_group, lp)

augment(fit) %>% 
	left_join(distinct(participants, participant, location)) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	filter(location=="Oxford") %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, aes(y = .fitted_prob), geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, aes(y = .fitted_prob), geom = "line", size = 1) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 title = "Oxford") +
	scale_y_continuous(limits = c(0, 1)) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

@@

# Appendix {.tabset .tab-pills}

@@

## {-}
